\Large \bf Polyglots : Crossing Origins by Crossing Formats

### 2013-05-03 main.tex
todo

%\documentclass{acm_proc_article-sp}
%\documentclass[10pt, conference, compsocconf]{IEEEtran}

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}

@@

% \author{\IEEEauthorblockN{Jonas Magazinius} 
% \IEEEauthorblockA{Department ofComputer Science\\ 
% Chalmers University of Technology\\ 
% Gothenburg, Sweden\\
% jonas.magazinius@chalmers.se} 
% \and 
% \IEEEauthorblockN{Billy Rios} 
% \IEEEauthorblockA{dept. name of organization\\ 
% name of organization, acronyms acceptable\\ 
% City, United States of America\\ 
% Email: name@xyz.com} 
% \and 
% \IEEEauthorblockN{Andrei Sabelfeld} 
% \IEEEauthorblockA{Department of Computer Science\\ 
% Chalmers University of Technology\\ 
% Gothenburg, Sweden\\ 
% andrei@chalmers.se} 
% }

@@

While these articles document known instances of polyglot attacks, the attack 
method has not been generalized until this paper.
%
Two attacker-centric components require special attention; the infiltration of 
an origin, i.e. the attack vector, and the exploitation of an infiltrated origin, i.e. the payload.
%In this situation, the same-origin policy is intended to prevent cross-origin 
%interaction.

@@

The reader is invited to visit the test page~\cite{Test:Page:12} for
practical demonstration of the concepts from this section.

@@

>>>>

\documentclass{sig-alternate}
%\documentclass[10pt, conference, compsocconf]{IEEEtran}
%\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{epsfig,endnotes}

@@

%\author{}
% \author{\IEEEauthorblockN{Jonas Magazinius} 
% \IEEEauthorblockA{Department ofComputer Science\\ 
% Chalmers University of Technology\\ 
% Gothenburg, Sweden\\
% jonas.magazinius@chalmers.se} 
% \and 
% \IEEEauthorblockN{Billy Rios} 
% \IEEEauthorblockA{dept. name of organization\\ 
% name of organization, acronyms acceptable\\ 
% City, United States of America\\ 
% Email: name@xyz.com} 
% \and 
% \IEEEauthorblockN{Andrei Sabelfeld} 
% \IEEEauthorblockA{Department of Computer Science\\ 
% Chalmers University of Technology\\ 
% Gothenburg, Sweden\\ 
% andrei@chalmers.se} 
% }

@@

While these articles document known instances of polyglot attacks, the attack 
method has not been generalized until this paper.
%
Under our generalization, previous work corresponds to
instances. For example, we show that GIFAR attacks describe a form of content smuggling, and
cross-origin CSS attacks describe a form of syntax injection attacks.
%
The added value of our paper is a generalized view and focus on new
instances of polyglots that involve the PDF format.

Two attacker-centric components require special attention; the infiltration of 
an origin, i.e. the attack vector, and the exploitation of an infiltrated origin, i.e. the payload.
%In this situation, the same-origin policy is intended to prevent cross-origin 
%interaction.

@@

The reader is invited to visit the test page~\cite{Test:Page:12} for
practical demonstration of the attacks from this section. These
attacks show that the vulnerabilities we focus on are exploitable in practice.

@@

Note that although some mitigation discussed below is already in place
(notably as implemented by the Chrome builtin PDF reader), the state of the art
is far from being satisfactory. As our paper demonstrates, the
polyglot attacks are a real threat. It is the paper's main value to
bring attention to polyglot attacks and the importance of
mitigation against them.
